Pillar 1 - Sequential Pattern Mining

### 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd
all course-student combinations

```
#Visualisation
It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful. We might need to sample. See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/

>>>>

#Visualisation
It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful. We might need to sample. See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/

#Puting students into take and not take.

```{r}
test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
  mutate(
    take_course = case_when(
      is.na(Grade)  ~ FALSE,
      T             ~ TRUE
      ),
    PFN = case_when(
      is.na(Grade)  ~ "not",
      Grade >= 5.5  ~ "pass",
      Grade < 5.5   ~ "fail"
      )
    )

table(test$PFN)
